GA3

### 2022-09-06 graphs_newt_snakes/GA3.Rmd
writing my interpretations

whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake-Newt Popsize", x_label="Snake-Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

>>>>

whale_gen(GA3_tall_tall_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```
